### 2014-04-15 doc/uist14/iteration2.tex
updated the iteration 2 results from today's study

We seek to quantify the improvement of such design and performed another user study to compare the {\em Binary IR} and {\em Valued IR} approaches. For this study, we aim to discover the performances at a denser environment. Thus, we take the 10 nodes and set it up in a smaller area (see Figure~\ref{fig:study-layout2}). In total, we have XX users for this study \ben{more information about users later.} Each user performs the target acquisition study 30 times for each approach. Similarly, half of them perform {\em Binary IR} first and the other half {\em Valued IR} first.

@@

\subsection{Evaluation}
Below is a summary of the study result.
\begin{enumerate}
\item Among the 150 trials in {\em Binary IR} condition, there are 104 times when disambiguation is needed. In {\em Valued IR} condition, only 65 out of 150 trials need disambiguation. We perform a Chi-square test on this result and the result is $\chi^2(1) = 20.611$, $p < 0.0001$. \ben{not sure about the degree of freedom being 1 here, will check later.} This demonstrates that the new approach successfully reduces the chances where disambiguation is needed.
\item In the cases when disambiguation is inevitable, the {\em Valued IR} will sort the list based on the intensity reading. As a result, out of the 65 times when disambiguation is involved, {\em Valued IR} sorts the desired target as the first one in the list 38 times (roughly 58\%). In comparison, for {\em Binary IR}, only 37 out of 104 (~35\%) times can the user find the desired target first in the list. Again a Chi-square test demonstrates the statistical differences (with $\chi^2(1) = 8.487$, $p = 0.0036$. 
\end{enumerate}

Such gain can be seen from Figure~\ref{fig:study2} where the overall target acquisition time is obtained. The average time is 4.32 seconds and 3.71 second for {\em Binary IR} and {\em Valued IR}, respectively; and a t-test shows that they are also significantly different $t(282)=2.0922$, $p=0.03$.

@@

However, one side effect that we have observed in this approach is that the {\em Valued IR} sometimes eliminates the desired target during the {\em coarse selection} stage. The rate is not high (16 out of 150 cases, ~10\%), but this is the trade-off for the overall faster acquisition time.

>>>>

We seek to quantify the improvement of such design and performed another user study to compare the {\em Binary IR} and {\em Valued IR} approaches. For this study, we aim to discover the performances at a denser environment. Thus, we take the 10 nodes and set it up in a smaller area (see Figure~\ref{fig:study-layout2}). In total, we have 10 users for this study, and each user performs 30 target acquisition tasks for each approach. Similarly to our first within-subject study, half of them perform {\em Binary IR} first and the other half {\em Valued IR} first.

@@

% new study results
% ceiling(c(nrow(name), nrow(name_multiple), wrong_guess, wrong_percentage * 100))
% intensity
%  300 167  74  45
% name
%  300 225 145  65

%% first one
%% 
%             Outcome 1	Outcome 2	     Total
% Group 1 	167	133	300
% Group 2	225	75	300
% Total	        392	208	600
%% Chi squared equals 24.755 with 1 degrees of freedom. 
%%  The two-tailed P value is less than 0.0001

% 	    Outcome 1	Outcome 2	     Total
% Group 1	74	93	167
% Group 2	145	80	225
% Total	        219	173	392
% Chi squared equals 15.758 with 1 degrees of freedom. 
%   The two-tailed P value is less than 0.0001

\subsection{Evaluation}
Below is a summary of the study result.
\begin{enumerate}
\item Among the 300 trials in {\em Binary IR} condition, there are 225 times when disambiguation is needed. In {\em Valued IR} condition, only 167 out of 300 trials need disambiguation. We perform a Chi-square test on this result and the result is $\chi^2(1) = 24.755$, $p < 0.0001$. This demonstrates that the new approach successfully reduces the chances where disambiguation is needed.
\item In the cases when disambiguation is inevitable, the {\em Valued IR} will sort the list based on the intensity reading. As a result, out of the 167 times when disambiguation is involved, {\em Valued IR} sorts the desired target as the first one in the list 93 times (roughly 55\%). In comparison, for {\em Binary IR}, only 80 out of 219 (35\%) times can the user find the desired target first in the list. Again a Chi-square test demonstrates the statistical difference (with $\chi^2(1) = 15.758$, $p < 0.0001$. 
\end{enumerate}

Such gain can be seen from Figure~\ref{fig:study2} where the overall target acquisition time is obtained. The average time is 4.31 seconds and 3.64 second for {\em Binary IR} and {\em Valued IR}, respectively; and a t-test shows that they are also significantly different $t(555)=3.2945$, $p=0.001$.

%  t.test(name$complete, intensity$complete)

% 	Welch Two Sample t-test

% data:  name$complete and intensity$complete
% t = 3.2945, df = 555.272, p-value = 0.001049
% alternative hypothesis: true difference in means is not equal to 0
% 95 percent confidence interval:
%  0.2707875 1.0704747
% sample estimates:
% mean of x mean of y 
%  4.311340  3.640709

@@

However, one side effect that we have observed in this approach is that the {\em Valued IR} sometimes eliminates the desired target during the {\em coarse selection} stage. The rate is not high (13 out of 300 cases, 4.3\%), but this is the trade-off for the overall faster acquisition time.
